Making ice sheet models \\ scale properly

### 2023-05-28 talk-oxford/slides.tex
move images/ to faciliate reuse

\titlegraphic{\hfill \includegraphics[width=0.15\textwidth]{images/uafbw.png}}

@@

{
  \usebackgroundtemplate{\includegraphics[width=\paperwidth]{images/gray-british-clark2022.png}}
  \begin{frame}
    \titlepage
  \end{frame}
}

@@

\bigskip
\begin{minipage}[t][60cm][t]{\textwidth}
\begin{center}
\includegraphics<1>[height=0.69\textheight]{images/ant-pittard2021.png}
\only<1>{\par {\scriptsize Antarctic ice sheet}} % (Pittard et al 2021)
\only<2>{\vspace{17mm}}
\includegraphics<2>[width=\textwidth]{images/ant-schoofhewitt2013.png}
\only<2>{\bigskip \hfill {\tiny (Schoof \& Hewitt 2013)}}
\only<2>{\vspace{4mm}}
\only<2>{\begin{center} {\footnotesize note vertical exaggeration, smooth surface, and rough bed} \end{center} }
\includegraphics<3>[height=0.69\textheight]{images/alps-seguinot2018.png}
\only<3>{\par {\scriptsize modeled Alpine ice sheet near last glacial maximum} \hfill {\tiny (Seguinot et al 2018)}}
\includegraphics<4>[height=0.69\textheight]{images/british-clark2022.png}
\only<4>{\par {\scriptsize modeled British-Irish ice sheet near last glacial maximum} \hfill {\tiny  (Clark et al 2022)}}
\includegraphics<5>[height=0.69\textheight]{images/not-sea-ice.png}
\only<5>{\par {\footnotesize an ice sheet is \emph{not} sea ice!}}
\end{center}
\end{minipage}
\end{frame}

@@

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item glacier ice is modeled as a \emph{very viscous, incompressible, non-Newtonian fluid}
    \begin{itemize}
    \item[$\circ$] more on that soon
    \end{itemize}
\item glaciers lie on \emph{topography}
    \begin{itemize}
    \item[$\circ$] sometimes they float  (\emph{ice shelf})
    \end{itemize}
\item glacier geometry and velocity evolve \emph{in contact with climate}:
    \begin{itemize}
    \item[$\circ$] snowfall
    \item[$\circ$] surface melt
    \item[$\circ$] subglacial melt
    \item[$\circ$] sub-shelf melt (when floating)
    \item[$\circ$] calving (into ocean)
    \end{itemize}
\end{itemize}
\end{column}
\begin{column}{0.42\textwidth}
\hfill \includegraphics[width=0.9\textwidth]{images/map-glacier-ice.png}
\end{column}
\end{columns}
\end{frame}

@@

\medskip
\item {\footnotesize see UAF's \href{https://pism.io/}{Parallel Ice Sheet Model (\texttt{pism.io})}, for example, as a model which includes these processes}
\end{itemize}
\end{column}
\begin{column}{0.42\textwidth}
\hfill \includegraphics[width=0.9\textwidth]{images/map-glacier-ice.png}
\end{column}
\end{columns}
\end{frame}

@@

\smallskip
\item {\small \alert{map}: \, $\begin{pmatrix} \text{climate \&} \\ \text{topography} \end{pmatrix} \to \begin{pmatrix} \text{geometry} \\ \text{\& velocity} \end{pmatrix}$ }
\end{itemize}
\end{column}
\begin{column}{0.42\textwidth}
\hfill \includegraphics[width=0.9\textwidth]{images/map-velocity.png}

@@

\vspace{-2mm}
\end{itemize}
\end{column}
\begin{column}{0.46\textwidth}
\includegraphics<1>[width=\textwidth]{images/domain-data.png}

\includegraphics<2>[width=\textwidth]{images/domain-surface.png}

\includegraphics<3>[width=\textwidth]{images/domain-velocity.png}
\end{column}
\end{columns}
\end{frame}

@@

\begin{center}
\includegraphics<1>[width=0.6\textwidth]{images/stokes-greens-arndt.png}
\includegraphics<2>[width=0.6\textwidth]{images/sia-greens-arndt.png}
\end{center}
\end{frame}

@@

\medskip
\begin{center}
\includegraphics[width=0.5\textwidth]{images/multigrid-grids.png}
\end{center}
\end{frame}

@@

\begin{center}
\includegraphics[width=0.6\textwidth]{images/isaac-antarctica.png}
\end{center}
    \item[$\circ$] $\alpha=0.05$ for Tuminaro et al~(2016) 1st-order (shallow) AMG solver
    \item[$\circ$] similar for Brown et al~(2013) 1st-order (shallow) GMG solver
    \end{itemize}
\end{itemize}
\end{frame}

@@

\vspace{3mm}
\begin{minipage}[t][60cm][t]{\textwidth}
\begin{center}
\only<1>{\includegraphics[height=0.52\textheight]{images/tiles-jouvet.png}}
\only<2>{\includegraphics[height=0.57\textheight]{images/cnn-jouvet.png}}
\end{center}
\end{minipage}
\end{frame}

>>>>

\titlegraphic{\hfill \includegraphics[width=0.15\textwidth]{../images/uafbw.png}}

@@

{
  \usebackgroundtemplate{\includegraphics[width=\paperwidth]{../images/gray-british-clark2022.png}}
  \begin{frame}
    \titlepage
  \end{frame}
}

@@

\bigskip
\begin{minipage}[t][60cm][t]{\textwidth}
\begin{center}
\includegraphics<1>[height=0.69\textheight]{../images/ant-pittard2021.png}
\only<1>{\par {\scriptsize Antarctic ice sheet}} % (Pittard et al 2021)
\only<2>{\vspace{17mm}}
\includegraphics<2>[width=\textwidth]{../images/ant-schoofhewitt2013.png}
\only<2>{\bigskip \hfill {\tiny (Schoof \& Hewitt 2013)}}
\only<2>{\vspace{4mm}}
\only<2>{\begin{center} {\footnotesize note vertical exaggeration, smooth surface, and rough bed} \end{center} }
\includegraphics<3>[height=0.69\textheight]{../images/alps-seguinot2018.png}
\only<3>{\par {\scriptsize modeled Alpine ice sheet near last glacial maximum} \hfill {\tiny (Seguinot et al 2018)}}
\includegraphics<4>[height=0.69\textheight]{../images/british-clark2022.png}
\only<4>{\par {\scriptsize modeled British-Irish ice sheet near last glacial maximum} \hfill {\tiny  (Clark et al 2022)}}
\includegraphics<5>[height=0.69\textheight]{../images/not-sea-ice.png}
\only<5>{\par {\footnotesize an ice sheet is \emph{not} sea ice!}}
\end{center}
\end{minipage}
\end{frame}

@@

\begin{columns}
\begin{column}{0.6\textwidth}
\begin{itemize}
\item glacier ice is modeled as a \emph{very viscous, incompressible, non-Newtonian fluid}
    \begin{itemize}
    \item[$\circ$] more on that soon
    \end{itemize}
\item glaciers lie on \emph{topography}
    \begin{itemize}
    \item[$\circ$] sometimes they float  (\emph{ice shelf})
    \end{itemize}
\item glacier geometry and velocity evolve \emph{in contact with climate}:
    \begin{itemize}
    \item[$\circ$] snowfall
    \item[$\circ$] surface melt
    \item[$\circ$] subglacial melt
    \item[$\circ$] sub-shelf melt (when floating)
    \item[$\circ$] calving (into ocean)
    \end{itemize}
\end{itemize}
\end{column}
\begin{column}{0.42\textwidth}
\hfill \includegraphics[width=0.9\textwidth]{../images/map-glacier-ice.png}
\end{column}
\end{columns}
\end{frame}

@@

\medskip
\item {\footnotesize see UAF's \href{https://pism.io/}{Parallel Ice Sheet Model (\texttt{pism.io})}, for example, as a model which includes these processes}
\end{itemize}
\end{column}
\begin{column}{0.42\textwidth}
\hfill \includegraphics[width=0.9\textwidth]{../images/map-glacier-ice.png}
\end{column}
\end{columns}
\end{frame}

@@

\smallskip
\item {\small \alert{map}: \, $\begin{pmatrix} \text{climate \&} \\ \text{topography} \end{pmatrix} \to \begin{pmatrix} \text{geometry} \\ \text{\& velocity} \end{pmatrix}$ }
\end{itemize}
\end{column}
\begin{column}{0.42\textwidth}
\hfill \includegraphics[width=0.9\textwidth]{../images/map-velocity.png}

@@

\vspace{-2mm}
\end{itemize}
\end{column}
\begin{column}{0.46\textwidth}
\includegraphics<1>[width=\textwidth]{../images/domain-data.png}

\includegraphics<2>[width=\textwidth]{../images/domain-surface.png}

\includegraphics<3>[width=\textwidth]{../images/domain-velocity.png}
\end{column}
\end{columns}
\end{frame}

@@

\begin{center}
\includegraphics<1>[width=0.6\textwidth]{../images/stokes-greens-arndt.png}
\includegraphics<2>[width=0.6\textwidth]{../images/sia-greens-arndt.png}
\end{center}
\end{frame}

@@

\medskip
\begin{center}
\includegraphics[width=0.5\textwidth]{../images/multigrid-grids.png}
\end{center}
\end{frame}

@@

\begin{center}
\includegraphics[width=0.6\textwidth]{../images/isaac-antarctica.png}
\end{center}
    \item[$\circ$] $\alpha=0.05$ for Tuminaro et al~(2016) 1st-order (shallow) AMG solver
    \item[$\circ$] similar for Brown et al~(2013) 1st-order (shallow) GMG solver
    \end{itemize}
\end{itemize}
\end{frame}

@@

\vspace{3mm}
\begin{minipage}[t][60cm][t]{\textwidth}
\begin{center}
\only<1>{\includegraphics[height=0.52\textheight]{../images/tiles-jouvet.png}}
\only<2>{\includegraphics[height=0.57\textheight]{../images/cnn-jouvet.png}}
\end{center}
\end{minipage}
\end{frame}
